A re-examination of the role of friction in the original Social Force Model

### 2019-05-28 paper.tex
agregue referencia al paper de zhang (empirical velocity profile)

We first noticed that low-density situations ($\rho<5$) lead to a cruising velocity profile $v=v_d$. This is valid for every location in the corridor (not only the center as was previously noticed in Section \ref{fundamental_diagram}). For higher densities($\rho>5$), the velocity profile turns into a parabola-like function. This shape resembles the usual velocity profile for laminar flow in a viscous fluid, where the velocity increases toward the center of a tube. In our case, pedestrians near the walls are the ones with the lower velocity. The velocity increases when departing from the wall until it reaches the maximum at the center of the corridor. This behavior suggests that the wall friction on the pedestrians, is playing a relevant role on the velocity distribution.\\

@@

\bibitem{Togashi1}
\textcolor{red}{Togashi, F., Misaka, T., L\"ohner, R., \& Obayashi, S. (2018). 
Using ensemble Kalman filter to determine parameters for computational crowd dynamics simulations. 
Engineering Computations, 35(7), 2612-2628.}

@@

>>>>

We first noticed that low-density situations ($\rho<5$) lead to a cruising velocity profile $v=v_d$. This is valid for every location in the corridor (not only the center as was previously noticed in Section \ref{fundamental_diagram}). For higher densities($\rho>5$), the velocity profile turns into a parabola-like function. This shape resembles the usual velocity profile for laminar flow in a viscous fluid, where the velocity increases toward the center of a tube. In our case, pedestrians near the walls are the ones with the lower velocity. The velocity increases when departing from the wall until it reaches the maximum at the center of the corridor. This behavior suggests that the wall friction on the pedestrians, is playing a relevant role on the velocity distribution. \textcolor{red}{The velocity profile is in accordance with the empirical measurements of Ref.~\cite{zhang1}.}  \\

@@

\bibitem{Togashi1}
\textcolor{red}{Togashi, F., Misaka, T., L\"ohner, R., and Obayashi, S. (2018). 
Using ensemble Kalman filter to determine parameters for computational crowd dynamics simulations. 
Engineering Computations, 35(7), 2612-2628.}

@@

\bibitem{zhang1}
\textcolor{red}{Zhang, X. L., Weng, W. G., Yuan, H. Y., and Chen, J. G. (2013). 
Empirical study of a unidirectional dense crowd during a real mass event. 
Physica A: Statistical Mechanics and its Applications, 392(12), 2781-2791.}
